---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ggraincloud

<!-- badges: start -->
[![R-CMD-check](https://github.com/bradfordjohnson/ggraincloud/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bradfordjohnson/ggraincloud/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**ggraincloud** is an R package that provides templated raincloud plots using the grammar of graphics with `ggplot2`. It streamlines the creation of visually appealing raincloud plots, combining density plots, boxplots, and scatter plots for enhanced data visualization. Perfect for users looking to create consistent and customizable raincloud plots efficiently.



## Installation

You can install the development version of ggraincloud from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("bradfordjohnson/ggraincloud")
```

## Examples

Create a raincloud plot using `raincloud()` and optionally style it with `theme_raincloud()`.

```{r example, fig.height=8, fig.width=6}
library(ggraincloud)

plot <- raincloud(iris, ggplot2::aes(Species, Sepal.Width), flip_coords = TRUE) +
  theme_raincloud(flip_coords = TRUE)

plot
```

Since the raincloud functions return a ggplot2 object, you can easily customize the plot by adding additional ggplot2 layers and functions.

```{r theme_void, fig.height=8, fig.width=6}
plot +
  ggplot2::theme_void()
```

You can place the "rain" (jittered points) inside the boxplot using `raincloud_boxjitter()`.

```{r boxjitter, fig.height=8, fig.width=6}
raincloud_boxjitter(
  iris,
  ggplot2::aes(
    Species,
    Sepal.Width,
    color = Species,
    fill = Species
  ),
  alpha = .5,
  flip_coords = FALSE
) +
theme_raincloud()
```

Use `raincloud_barcode()` to display barcode lines instead of jittered points.

```{r barcode, fig.height=8, fig.width=6}
raincloud_barcode(iris, ggplot2::aes(Species, Sepal.Width), barcode_size = 10) +
  theme_raincloud()
```

## Acknowledgments

The `ggraincloud` package was inspired by the work of [Cédric Scherer](https://www.cedricscherer.com/). His shared code snippets and creative variations of raincloud plots in R sparked the idea to develop this package, making it easier to quickly create raincloud plots using ggplot2. A huge thanks to Cédric for his invaluable contributions to the R and data visualization community!
