---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ggraincloud

<!-- badges: start -->
[![R-CMD-check](https://github.com/bradfordjohnson/ggraincloud/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bradfordjohnson/ggraincloud/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

**ggraincloud** is an R package that provides templated raincloud plots using the grammar of graphics with `ggplot2`. It streamlines the creation of visually appealing raincloud plots, combining density plots, boxplots, and scatter plots for enhanced data visualization. Perfect for users looking to create consistent and customizable raincloud plots efficiently.



## Installation

You can install the development version of ggraincloud from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("bradfordjohnson/ggraincloud")
```

## Example

Create a raincloud plot using `raincloud()`.

```{r example, fig.height=8, fig.width=6}
library(ggraincloud)

raincloud(iris, ggplot2::aes(Species, Sepal.Width), flip_coords = TRUE) +
  ggplot2::theme_minimal()

raincloud(
  iris,
  ggplot2::aes(
    Species,
    Sepal.Width,
    color = Species,
    fill = Species
  ),
  alpha = .5,
  flip_coords = FALSE
) +
ggplot2::theme_minimal()
```
